---
title: "Data analysis with Grow-Shrink and Hill-Climb Algorithms"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{bnanalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
devtools::load_all(".")
```
### Dominik Kunz
### 20.09.21

## Introduction
This vigniette gives a high level overview on the potential use of the bnanalysis
library R package. The package consists of two functions:\
1. hcanalysis(): Data analysis via hill-climbing algorithm \
2. gsanalysis(): Data analysis via grow-shrink algorithm \


```{r}
library(bnanalysis)
```

## Data Input
To run the analysis the R Package needs input data in the form of a data frame

```{r setup, include=FALSE}
knitr::opts_chunk$set(dpi=100,fig.width=5)
```

## Generating Output
The output presents missing connections between nodes (red), and returns a summary
of the model.
```{r}
gsanalysis(iris)
```

If there are no connections missing the model will simply plot the model structure
and list a model summary
```{r}
hcanalysis(iris)
```

